Supplemental Materials for ``Universals of word order result from optimization of grammars for efficient communication''

### 2019-05-25 second-draft/pnas-word-order-si.tex
SI

@@

In our experiments, we chose $\lambda = 0.9$ as a mathematically valid value that puts similar weight on both predictability and parseability.
The computational cost of grammar optimization precluded repeating the experiment for many values of $\lambda$.
We note that each of the eight correlations is predicted by at least parseability or predictability, without any contradictory predictions (Table~\ref{tab:all-predictions-1}).
%Indeed, the same holds for all of the 38 syntactic relations in UD  (Table~\ref{tab:all-predictions-1}-\ref{tab:all-predictions-2})
%We additionally report results with $\lambda = 0$, i.e., placing all weight on parseability.
That is, at $\lambda$ close to its maximal value, the predictions of optimizing the two scoring functions individually add up to the predictions of efficiency optimization.
Small values of $\lambda$ correspond to the case where predictability plays no role, and only parseability is optimized (Table~\ref{tab:all-predictions-1}).
We also verified the robustness of our results to small variations of $\lambda$, by reporting results with $\lambda=1$ in Table~\ref{table:corr-resu-previous}.

@@

In this section, we describe the details of the neural network architectures.
Choices follow standard practice and machine learning and were fixed before evaluating word order properties, and the efficiency of real languages.

>>>>

\textcolor{red}{notation U, L(T)}

\textcolor{red}{run czech parser}

\textcolor{red}{run controls on additional random grammars}

@@

In our experiments, we chose $\lambda = 0.9$ as a mathematically valid value that puts similar weight on both predictability and parseability.
The computational cost of grammar optimization precluded repeating the experiment for many values of $\lambda$.
To tease apart the relative contributions of the two components, we also examine word order predictions for grammars optimized only to optimize parseability, or only predictability.
As shown in Table~\ref{tab:all-predictions-1}, each of the eight correlations is predicted by at least parseability or predictability, without any contradictory predictions.
%Indeed, the same holds for all of the 38 syntactic relations in UD  (Table~\ref{tab:all-predictions-1}-\ref{tab:all-predictions-2})
%We additionally report results with $\lambda = 0$, i.e., placing all weight on parseability.
That is, at $\lambda$ close to its maximal value, the predictions of optimizing the two scoring functions individually add up to the predictions of efficiency optimization.
Small values of $\lambda$ correspond to the case where predictability plays no role, and only parseability is optimized (Table~\ref{tab:all-predictions-1}), in which case not all correlations are predicted (Figure~\ref{fig:posterior}).
We also verified the robustness of our results to small variations of $\lambda$, by reporting results with $\lambda=1$ in Table~\ref{table:corr-resu-previous}.

@@

In this section, we describe the details of the neural network architectures.
Choices follow standard practice in machine learning and were fixed before evaluating word order properties, and the efficiency of real languages.
